The Impact of Alternation

### 2017-08-16 arxiv/draft.tex
added arxiv

\begin{figure}[htb]
\vspace*{-\baselineskip}
\centerline{\includegraphics[scale=0.8]{figures/Example.pdf}}
\vspace*{-\baselineskip}
\caption{Alternating Data Automaton Example}
\label{fig:ex}
\end{figure}

@@

\begin{figure}[t!]
\begin{tabular}{cc}
\includegraphics[scale=0.5]{figures/PA1.pdf} & \includegraphics[scale=0.5]{figures/PA2.pdf} \\[-2mm]
\tiny{(a)} & \tiny{(b)} \\
\\
\includegraphics[scale=0.5]{figures/PA3.pdf} & \includegraphics[scale=0.5]{figures/PA4.pdf} \\[-2mm]
\tiny{(c)} & \tiny{(d)}
\end{tabular}
\vspace*{-\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex} by Algorithm \ref{alg:predabs}}
\label{fig:pa}
\end{figure}

@@

\begin{figure}[htb]
\vspace*{-\baselineskip}
\begin{tabular}{c}
\includegraphics[scale=0.65]{figures/IM1.pdf} \\
\tiny{(a)} \\
\includegraphics[scale=0.65]{figures/IM2.pdf} \\[-2mm]
\tiny{(b)} \\
\includegraphics[scale=0.65]{figures/IM3.pdf} \\[-2mm]
\tiny{(c)}
\end{tabular}
\vspace*{-0.5\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex}
  by Algorithm \ref{alg:impact} (1/2)}
\label{fig:im1}
\vspace*{-\baselineskip}
\end{figure}

\begin{figure}[htb]
\centerline{\includegraphics[scale=0.65]{figures/IM4.pdf}}
\vspace*{-\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex}
  by Algorithm \ref{alg:impact} (2/2)}
\label{fig:im2}
\end{figure}

@@

\begin{table}[htb]
\begin{center}
{\fontsize{8}{9}\selectfont
\begin{tabular}{||l|c|c|c|c|c||}
\hline
Example & $\len{\A}$ & $L(\A)=\emptyset$ ? & Algorithm \ref{alg:predabs} & Algorithm \ref{alg:impact} & \textsc{Includer} \\
\hline
simple1 & 321 & no & 0.576 & 0.061 & 0.021\\
\hline
simple2 & 520 & yes & 0.598 & 0.179 & 0.031\\
\hline
simple3 & 220 & yes & 0.702 & 0.144 & 0.051\\
\hline
array\_shift & 884 & yes & 1.88 & 0.199 & 0.060\\
\hline
array\_simple & 3456 & yes & timeout & 13.421 & 5.496\\
\hline
array\_rotation1 & 1848 & yes & 5.677 & 0.798 & 0.114\\
\hline
array\_rotation2 & 15208 & yes & timeout & timeout & 23.056\\
\hline
abp & 6965 & no & 7.538 & 1.111 & 1.715\\
\hline
train & 1875 & yes & 13.39 & 2.236 & 0.308\\
\hline
hw1 & 332 & yes & 1.101 & 0.22 & 0.159\\
\hline
hw2 & 690 & yes & 18.536 & 0.446 & 0.419\\
\hline
\end{tabular}
}
\caption{}\label{tab:experiments}
\end{center}
\end{table}

>>>>

\begin{figure}[htb]
\vspace*{-\baselineskip}
\centerline{\includegraphics[scale=0.8]{Example.pdf}}
\vspace*{-\baselineskip}
\caption{Alternating Data Automaton Example}
\label{fig:ex}
\end{figure}

@@

\begin{figure}[t!]
\begin{tabular}{cc}
\includegraphics[scale=0.5]{PA1.pdf} & \includegraphics[scale=0.5]{PA2.pdf} \\[-2mm]
\tiny{(a)} & \tiny{(b)} \\
\\
\includegraphics[scale=0.5]{PA3.pdf} & \includegraphics[scale=0.5]{PA4.pdf} \\[-2mm]
\tiny{(c)} & \tiny{(d)}
\end{tabular}
\vspace*{-\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex} by Algorithm \ref{alg:predabs}}
\label{fig:pa}
\end{figure}

@@

\begin{figure}[htb]
\vspace*{-\baselineskip}
\begin{tabular}{c}
\includegraphics[scale=0.65]{IM1.pdf} \\
\tiny{(a)} \\
\includegraphics[scale=0.65]{IM2.pdf} \\[-2mm]
\tiny{(b)} \\
\includegraphics[scale=0.65]{IM3.pdf} \\[-2mm]
\tiny{(c)}
\end{tabular}
\vspace*{-0.5\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex}
  by Algorithm \ref{alg:impact} (1/2)}
\label{fig:im1}
\vspace*{-\baselineskip}
\end{figure}

\begin{figure}[htb]
\centerline{\includegraphics[scale=0.65]{IM4.pdf}}
\vspace*{-\baselineskip}
\caption{Proving Emptiness of the Automaton from Fig. \ref{fig:ex}
  by Algorithm \ref{alg:impact} (2/2)}
\label{fig:im2}
\end{figure}

@@

\begin{table}[htb]
\begin{center}
{\fontsize{8}{9}\selectfont
\begin{tabular}{||l|c|c|c|c|c||}
\hline
Example & $\len{\A}$ & $L(\A)=\emptyset$ ? & Algorithm \ref{alg:predabs} & Algorithm \ref{alg:impact} & \textsc{Includer} \\
\hline
simple1 & 309 & no & 0.641 & 0.061 & 0.021\\
\hline
simple2 & 504 & yes & 0.667 & 0.179 & 0.031\\
\hline
simple3 & 214 & yes & 0.825 & 0.150 & 0.051\\
\hline
array\_shift & 874 & yes & 2.138 & 0.209 & 0.060\\
\hline
array\_simple & 3440 & yes & timeout & 16.435 & 5.496\\
\hline
array\_rotation1 & 1834 & yes & 6.827 & 0.865 & 0.114\\
\hline
array\_rotation2 & 15182 & yes & timeout & timeout & 23.056\\
\hline
abp & 6909 & no & 8.292 & 1.410 & 1.715\\
\hline
train & 1823 & yes & 16.989 & 2.738 & 0.308\\
\hline
hw1 & 322 & yes & 1.566 & 0.298 & 0.159\\
\hline
hw2 & 674 & yes & 22.914 & 0.552 & 0.419\\
\hline
\end{tabular}
}
\caption{}\label{tab:experiments}
\end{center}
\end{table}
